The SMT Competition 2015--2018

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Layout and clean up main track winners tables for families and unknown.

\begin{table}
\caption{Alternative winners if families were not used in computing scores e.g. the 2015 scoring system were used.\label{tab:results:total:solved}}
\centering
\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
\toprule
Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
\hline\hline
AUFNIRA &   & CVC4  &   &   \\
UFIDL   &   & \nc{Z3}  &   &   \\
BV      &   &   & Boolector  &   \\
QF\_LRA  &   &   & Yices2  & SPASS-SATT  \\
QF\_NIA  &   &   & Yices2  & Yices2  \\
QF\_BV   &   &   &   & Boolector  \\
QF\_FP   &   &   &   & CVC4  \\
\bottomrule
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%
\subsection{What Impact Did Adding Unknowns Have?}

@@

\begin{table}
\caption{Alternative winners if benchmarks with unknown status had not bee included in 2017 onwards.\label{tab:results:unknowns}}
\centering
\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
\toprule
Division                       &  2017                  &  2018                      \\
\hline\hline
AUFNIRA & CVC4 & \\
QF\_NIRA & \nc{Z3} & CVC4 \nc{Z3} \\
QF\_NRA & \nc{Z3} & \\
UFDTLIA & CVC4 & \\
BV & & Boolector \\
QF\_FP & & CVC4 \nc{Z3} \\
UFNIA & & CVC4 \\
NRA & & -/\nc{Z3} \\
UF & & -/CVC4\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\input{table-winners-main-families}
%%%%%%%%%%%%%%%%%
\subsection{What Impact Did Adding Unknowns Have?}

@@

\input{table-winners-main-unknown}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-04-14 2018/report/table-winners-main-families.tex
Report: Layout and clean up main track winners tables for families and unknown.

\begin{table}
  \caption{Alternative best solvers in the Main track if only \emph{satisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}
  \label{tab:results:sat}
\centering
  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
    \toprule
    Division         &  2015                &  2016                   &  2017                   &  2018                     \\
    \hline \hline
    ALIA             &                      &                         &                         & \cc{alt} Alt-Ergo         \\
    AUFLIA           & \cc{cvc3} CVC3       &                         &                         & \cc{alt} Alt-Ergo         \\
    AUFLIRA          &                      & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{alt} Alt-Ergo         \\
    AUFNIRA          & \nonc\nc{Z3}         & \cc{cvc4} CVC4 \nc{Z3}  & \cc{cvc4} CVC4 \nc{Z3}  & \nc{Z3}                   \\
    BV               &                      & \nc{Z3}                 & \cc{bool} Boolector     & \cc{bool} Boolector       \\
    LRA              &                      &                         & \cc{verit} veriT        &                           \\
    NIA              & \nonc \cc{cvc3} CVC3 &                         &                         &                           \\
    NRA              & \nonc \cc{cvc3} CVC3 & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{cvc4} CVC4 \nc{Z3}    \\
    QF\_ABV          &                      & \cc{yices} Yices2       & \cc{yices} Yices2       &                           \\
    QF\_AUFBV        & \cc{yices} Yices     & \cc{yices} Yices2       &                         & \cc{yices} Yices2         \\
    QF\_BV           &                      & \nc{Z3}/MinkeyRink      &                         &                           \\
    QF\_FP           &                      &                         &                         & \cc{cvc4} CVC4            \\
    QF\_LIA          & \nc{Z3}              &                         &                         &                           \\
    QF\_LRA          &                      &                         & \cc{yices} Yices2       & \cc{yices} Yices2         \\
    QF\_NIA          &                      & \cc{rat} SMT-RAT        &                         &                           \\
    QF\_NIRA         &                      &                         & \cc{cvc4} CVC4          &                           \\
    QF\_NRA          &                      &                         & \nc{Z3}                 &                           \\
    QF\_UFBV         &                      &                         &                         & \cc{yices} Yices2         \\
    QF\_UFIDL        & \nc{Z3}              & \nc{Z3}                 & \nc{Z3}                 & \cc{verit} veriT  \nc{Z3} \\
    QF\_UFNIA        & \nonc \cc{cvc3} CVC3 &                         & \cc{cvc4} CVC4          &                           \\
    UF               &                      & \cc{vamp} Vampire       &                         & \cc{vamp}Vampire/-        \\
    UFBV             &                      & \cc{bool} Boolector     &                         &                           \\
    UFDTLIA          &                      &                         & \nonc \cc{cvc4} CVC4    &                           \\
    UFLIA            & \nc{Z3}              &                         &                         &                           \\
    UFLRA            & \cc{cvc3} CVC3       & \cc{cvc4} CVC4          &                         &                           \\
    UFNIA            &                      & \cc{cvc4} CVC4          & \cc{cvc4} CVC4          & \cc{cvc4} CVC4            \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}
  \caption{Alternative best solvers in the Main track if only \emph{unsatisfiable} benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.}
  \label{tab:results:unsat}
  \centering
  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
\toprule
Division        &  2015                  &  2016                     &  2017                 &  2018                   \\
\hline \hline
    BV          &                        & \cc{cvc4} CVC4            &                       &                         \\
    NIA         &                        & \cc{cvc4} CVC4            & \cc{vamp} Vampire     & \cc{vamp} Vampire       \\
    QF\_AUFBV   &                        &                           & \cc{cvc4} CVC4        &                         \\
    QF\_AUFNIA  & \nonc \nc{Z3}          & \nonc \nc{Z3}             &                       &                         \\
    QF\_BV      &                        &                           & -/Boolector           &                         \\
    QF\_IDL     & \cc{cvc4} CVC4         &                           & \nc{Z3}               & \cc{cvc4} CVC4 \nc{Z3}  \\
    QF\_LIA     & \cc{smti} SMTInterpol  & \cc{smti} SMTInterpol     & \cc{smti} SMTInterpol & \cc{smti} SMTInterpol   \\
    QF\_NIA     & \cc{cvc3} CVC3         &                           & \cc{yices} Yices2     &                         \\
    QF\_NRA     &                        &                           &                       & \cc{cvc4} CVC4          \\
    QF\_UFLIA   &                        &                           & \nc{Z3}               &                         \\
    QF\_UFNRA   &                        & \cc{cvc4} CVC4 \nc{Z3}    & \cc{cvc4} CVC4        & \cc{cvc4} CVC4 \nc{Z3}  \\
    UF          &                        &                           & \cc{cvc4} CVC4        & -/CVC4                  \\
    UFIDL       &                        & \cc{vamp} Vampire \nc{Z3} & \nc{Z3}               &                         \\
    UFLRA       &                        &                           & \cc{verit} veriT      & \cc{verit} veriT        \\
    \bottomrule
  \end{tabular}

\end{table}

>>>>

\begin{table}
  \caption{Alternative best solvers in the Main track if families were not considered in computing scores (i.e., the 2015 scoring system were used).}
  \label{tab:results:total:solved}
  \centering
  \begin{tabular}{r@{\hskip 1em}>{\columncolor{white}[.25em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][.5em]}c@{\hskip 1em}>{\columncolor{white}[.5em][0.5em]}c}
    \toprule
    Division & 2015 &  2016           &  2017                &  2018                  \\
    \hline\hline
    AUFNIRA  &      & \cc{cvc4} CVC4  &                      &                        \\
    UFIDL    &      & \nc{Z3}         &                      &                        \\
    BV       &      &                 & \cc{bool} Boolector  &                        \\
    QF\_LRA  &      &                 & \cc{yices} Yices2    & \cc{spass} SPASS-SATT  \\
    QF\_NIA  &      &                 & \cc{yices} Yices2    & \cc{yices} Yices2      \\
    QF\_BV   &      &                 &                      & -/Boolector            \\
    QF\_FP   &      &                 &                      & \cc{cvc4} CVC4         \\
  \bottomrule
  \end{tabular}
\end{table}
